---
title: "p8105_hw3_tl2882"
author: "Tian Li"
date: 2018-10-09
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 8,
  fig.asp = 1,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

```{r install_github_dataset}
# install.packages("devtools")
devtools::install_github("p8105/p8105.datasets")
library(p8105.datasets)
```

# Problem 1

## Read and clean brfss_smart2010

```{r Read_and_clean_brfss_smart2010}
brfss = brfss_smart2010 %>% 
  janitor::clean_names() %>%
  filter(topic == "Overall Health") %>% 
  mutate(response = factor(response, levels = c("Excellent", "Very good", "Good", "Fair", "Poor"))) %>% 
  arrange(year, locationdesc, response)
```

## Problem 1.1

```{r Problem_1_1}
brfss %>%  
  filter(year == "2002") %>% 
  group_by(locationabbr) %>%
  summarize(n_locations = n_distinct(locationdesc)) %>% 
  filter(n_locations == 7)
```

In 2002, CT, FL, and NC states were observed at 7 locations.

## Problem 1.2

```{r Problem_1_2}
brfss %>%  
  group_by(year, locationabbr) %>%
  summarize(n_locations = n_distinct(locationdesc)) %>%
  ggplot(aes(x = year, y = n_locations, color = locationabbr)) + 
    geom_line() + 
    labs(title = "The number of locations in each state from 2002 to 2010",
         x = "Year", 
         y = "Number of locations", 
         caption = "Data from the p8105.datasets") + 
    viridis::scale_color_viridis(name = "State", discrete = TRUE) +
    theme(legend.position = "right")
```

This is the “spaghetti plot” that shows the number of locations in each state from 2002 to 2010.  
Y is "Number of observations", X is "Year", and each line represents a different state.

## Problem 1.3

```{r Problem_1_3}
brfss %>%  
  filter(year == "2002" | year == "2006" | year == "2010") %>% 
  filter(locationabbr == "NY", response == "Excellent") %>%
  group_by(year) %>% 
  summarize(excellent_mean = mean(data_value),
            excellent_sd = sd(data_value)) %>% 
  knitr::kable(digits = 1)
```

This is the table showing, for the years 2002, 2006, and 2010, the mean (as in "excellent_mean") and standard deviation (as in "excellent_sd") of the proportion of “Excellent” responses across locations in NY State.

## Problem 1.4

```{r Problem_1_4}
brfss %>% 
  group_by(year, locationabbr, response) %>% 
  summarize(proportion_mean = mean(data_value)) %>% 
  ggplot(aes(x = year, y = proportion_mean, color = locationabbr)) + 
    geom_line() + 
    labs(
      title =
        "Distribution of these state-level averages over time (for each response separately)",
      caption = "Data from the p8105.datasets") + 
    theme(axis.text.x = element_text(angle = 90)) +
    facet_grid(~response) + 
    viridis::scale_fill_viridis(discrete = TRUE)
```

* I chose "geom_line" because line chart shows the trend of data at equal time intervals, which reflects the distribution of these state-level averages over time best.

This is the five-panel plot that shows, for each response category separately, the distribution of these state-level averages over time.


# Problem 2

```{r exploration}
head(instacart)
```

## Exploration of this dataset

This is data from a deliver company named Instacart.

It is a 1,384,617 rows X 15 columns data frame, which means it has 1,384,617 observations and 15 variables.

The tpypes of "eval_set", "product_name", "aisle" and "department" are "character", others are "int".

Key variable: "order_id" and "product_id".  
With the order ID and product ID (or product name), we can specify every observation.

Illustrative examples of observations:  
For example,  
for order ID 1 (order number 4), it means that a person (user ID 112108) orderd 8 items at 10:00, Thursday, 9 days after last order.

Those items are: "Bulgarian Yogurt", "Organic 4% Milk Fat Whole Milk Cottage Cheese", "Organic Celery Hearts", "Cucumber Kirby", "Lightly Smoked Sardines in Olive Oil", "Bag of Organic Bananas", "Organic Hass Avocado", "Organic Whole String Cheese".

They are from aisle "yogurt", "other creams cheeses", "fresh vegetables", "fresh vegetables", "canned meat seafood", "fresh fruits", "fresh fruits", "packaged cheese" respectively.

They are from department "dairy eggs", "dairy eggs", "produce", "produce", "canned goods", "produce", "produce", "dairy eggs" respectively.

## Problem 2.1

```{r Problem_2_1}
unique(instacart$aisle) %>% 
  length()
  
instacart %>% 
  count(aisle) %>% 
  filter(min_rank(desc(n)) == 1)
```

There are 134 aisles, and the "fresh vegetables" is the most items ordered from.

## Problem 2.2

```{r Problem_2_2}
library(patchwork)

p1 =
  instacart %>% 
  filter(aisle_id <= 15) %>% 
  ggplot(aes(x = factor(aisle_id))) + ylim(0,151000) + 
    geom_bar() +
    labs(title = "Number of items
in each aisle (ID 1-15)") 
    
p2 =
  instacart %>% 
  filter(aisle_id > 15, aisle_id <= 30) %>% 
  ggplot(aes(x = factor(aisle_id))) + ylim(0,151000) + 
    geom_bar() + 
    labs(title = "Number of items 
in each aisle (ID 16-30)")

p3 =
  instacart %>% 
  filter(aisle_id > 30, aisle_id <= 45) %>% 
  ggplot(aes(x = factor(aisle_id))) + ylim(0,151000) + 
    geom_bar() + 
    labs(title = "Number of items
in each aisle (ID 31-45)") 

p4 =
  instacart %>% 
  filter(aisle_id > 45, aisle_id <= 60) %>% 
  ggplot(aes(x = factor(aisle_id))) + ylim(0,151000) + 
    geom_bar() + 
    labs(title = "Number of items
in each aisle (ID 46-60)")

p5 =
  instacart %>% 
  filter(aisle_id > 60, aisle_id <= 75) %>% 
  ggplot(aes(x = factor(aisle_id))) + ylim(0,151000) + 
    geom_bar() + 
    labs(title = "Number of items
in each aisle (ID 61-75)") 

p6 =
  instacart %>% 
  filter(aisle_id > 75, aisle_id <= 90) %>% 
  ggplot(aes(x = factor(aisle_id))) + ylim(0,151000) + 
    geom_bar() + 
    labs(title = "Number of items
in each aisle (ID 77-90)")

p7 =
  instacart %>% 
  filter(aisle_id > 90, aisle_id <= 105) %>% 
  ggplot(aes(x = factor(aisle_id))) + ylim(0,151000) + 
    geom_bar() + 
    labs(title = "Number of items
in each aisle (ID 91-105)")

p8 =
  instacart %>% 
  filter(aisle_id > 105) %>% 
  ggplot(aes(x = factor(aisle_id))) + ylim(0,151000) + 
    geom_bar() + 
    labs(title = "Number of items
in each aisle (ID 106-134)")

(p1 | p2 | p3) / (p4 | p5 | p6) / (p7 | p8)
```

* I chose "geom_bar" because it can show the number of items in each aisle most clearly.  
Because there are too many aisles, I separate them to 8 figures according to the aisle ID. And  I make sure that the limits of y are all (0,151000).

This is the plot that shows the number of items ordered in each aisle.

## Problem 2.3

```{r Problem_2_3}
instacart %>% 
  filter(aisle == "baking ingredients" | aisle == "dog food care" | 
         aisle == "packaged vegetables fruits") %>% 
  group_by(aisle, product_name) %>% 
  summarize(n = n()) %>% 
  filter(min_rank(desc(n)) == 1) %>% 
  knitr::kable(digits = 1)
```

This is the table showing the most popular item in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”.

## Problem 2.4

```{r Problem_2_4}
instacart %>% 
  filter(product_name == "Pink Lady Apples" | product_name == "Coffee Ice Cream") %>% 
  group_by(product_name, order_dow) %>% 
  summarise(mean_hour = mean(order_hour_of_day)) %>% 
  spread(key = order_dow, value = mean_hour) %>% 
  rename('Sun.' = '0', 'Mon.' = '1', 'Tues.' = '2', 'Wed.' = '3', 'Thur' = '4', 
         'Fri.' = '5', 'Sat.' = '6') %>% 
  knitr::kable(digits = 1)
```

This is the table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week.
