---
title: "p8105_hw3_tl2882"
author: "Tian Li"
date: 2018-10-09
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = 1,
  out.width = "90%"
)

theme_set(theme_bw() + theme(legend.position = "bottom"))
```

```{r install_github_dataset}
# install.packages("devtools")
devtools::install_github("p8105/p8105.datasets")
library(p8105.datasets)
```

# Problem 1

## Read and clean brfss_smart2010

```{r Read_and_clean_brfss_smart2010}
brfss = brfss_smart2010 %>% 
  janitor::clean_names() %>%
  filter(topic == "Overall Health") %>% 
  mutate(response = factor(response, levels = c("Excellent", "Very good", "Good", "Fair", "Poor"))) %>% 
  arrange(year, locationdesc, response)
```

## Problem 1.1

```{r Problem_1_1}
brfss %>%  
  filter(year == "2002") %>% 
  group_by(locationabbr) %>%
  summarize(n_locations = n_distinct(locationdesc)) %>% 
  filter(n_locations == 7)
```

In 2002, CT, FL, and NC states were observed at 7 locations.

## Problem 1.2

```{r Problem_1_2}
brfss %>%  
  group_by(year, locationabbr) %>%
  summarize(n_locations = n_distinct(locationdesc)) %>%
  ggplot(aes(x = year, y = n_locations, color = locationabbr)) + 
    geom_line() + 
    labs(title = "The number of locations in each state from 2002 to 2010",
         x = "Year", 
         y = "Number of locations", 
         caption = "Data from the p8105.datasets") + 
    viridis::scale_color_viridis(name = "State", discrete = TRUE) +
    theme(legend.position = "right")
```

This is the “spaghetti plot” that shows the number of locations in each state from 2002 to 2010.  
Y is "Number of observations", X is "Year", and each line represents a different state.

## Problem 1.3

```{r Problem_1_3}
brfss %>%  
  filter(year == "2002" | year == "2006" | year == "2010") %>% 
  filter(locationabbr == "NY", response == "Excellent") %>%
  group_by(year) %>% 
  summarize(excellent_mean = mean(data_value),
            excellent_sd = sd(data_value)) %>% 
  knitr::kable(digits = 1)
```

This is the table showing, for the years 2002, 2006, and 2010, the mean (as in "excellent_mean") and standard deviation (as in "excellent_sd") of the proportion of “Excellent” responses across locations in NY State.
